Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2015-09-09 gel_cond/trunk/paper.tex
rephrase the description of the c+p mixture

We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level. For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is sterically stabilised causing nearly hard sphere repulsion at contact. We use sterically stabilised particles of diameter $\sigma=\SI{3}{\micro\metre}$ in a refractive index matching and density matching mixture of organic solvents. In weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}. The short ranged, $\sigma/10$, depletion attraction caused by non-adsorbing polymers is masked by the electrostatic repulsion.

>>>>

We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level. For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is also sterically stabilised causing nearly hard sphere repulsion at contact. We disperse colloidal particles and non-adsorbing polymers in a  mixture of organic solvents that matches both the refractive index and the density of the particles. In such weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}, here diameter $\sigma=\SI{3}{\micro\metre}$. The short ranged, $\sigma/10$, depletion attraction caused by the polymers is masked by the electrostatic repulsion.
